---
title: "Chemical Engineering Laboratory Data"
output:
  html_document
---

```{r setup, include=FALSE}

## Turn off auto-code display in Markdown and load libraries.Note, if you do not already have 'DT' installed, input install.packages(DT) into the command line and install the package before running this code.

knitr::opts_chunk$set(echo = FALSE)

library(DT)
```

## Retrieve Data

Change the values in the code below to import your data into R. You will need to enter inputs for the following variables: 

  - startdate
  - enddate
  - starttime
  - endtime
  - area
  - interval
  

```{r import, echo=TRUE}

## Change these values

## Use YYYY-MM-DD date format.
startdate <- '2022-03-16'
enddate <- '2022-03-16'

## Use 24-hour clocks (e.g. 2:00PM is 14:00). All times are local to RHIT. Up to 24 hours of data may be requested at a time.
starttime <- '14:00'
endtime <- '16:50'

## For area designations, 150 is Reverse Osmosis, 300 is Fluid Flow, etc.
area <- '150'

## Sampling data every 30 sections ('30s') is most common, but other values may be chosen.
interval <- '30s'
```

```{r call_data}

## This code creates the URL for data retrieval. You should not need to edit this code.

URL_base <- 'https://uolab.rose-hulman.edu/csv?'

data_URL <- paste(URL_base,
                  'startdate=', startdate,
                  '&starttime=', starttime, 
                  '&enddate=', enddate,
                  '&endtime=', endtime,
                  '&interval=', interval,
                  '&area=', area,
                  sep = '')

## Save retrieved data as a data frame.
df <- read.csv(url(data_URL))

```
\
Based on your inputs, the following URL (`data_URL`) was generated to retrieve your data. Clicking on the link will download the csv file, which is useful if you would prefer to work with the data outside of R.
\
\
`r toString(data_URL)`  

\

## Data Summary
The retrieved data contains `r nrow(df)` rows and `r ncol(df)` columns and is shown in the table below. Use the search bar and/or filters below each column (click the boxes that say 'all') to quickly puruse the data. *You can perform additional data manipulation in R using this data (saved as variable `df`).*
\
\

```{r}

## Summarize data in table that contains column filters.

datatable(data = df, 
          filter = "top")
```